Simulation of angular resolution of a new electromagnetic sampling calorimeter

### 2023-01-26 paper.tex
updates

The toy sampling calorimeter is designed as a block consisting of alternating layers of an 1-mm-thick lead absorber and a 5-mm-thick polyvinyltoluene-based plastic scintillator. The plastic scintillator is segmented into 15-mm-wide strips, which are alternately oriented in the vertical and horizontal directions, as shown in Figure~\ref{fig:det_conf}. It has a cross-section size of 525~$\times$~525~mm$^{2}$ and accommodates 105 alternating layers of 630~mm and 20 radiation lengths (20$X_{0}$) to contain the EM showers for energies in the range of 0.1 to 2~GeV.

@@

The incident angle of the photons is reconstructed using XGB~\cite{xgboost:2016}, which maps a feature dataset, the energy deposit in each scintillator strip, onto a target variable, the incident angle of a photon. The feature size identical to the number of strips varies with the strip width to have the same coverage. In the case of the 15-mm-wide strips, 35~$\times$~105 channels compose the detector. XGB constructs gradient-boosted decision trees using the training dataset, efficiently descending the loss function. The hyperparameter of XGB is the parameter driving how models are trained. In this paper, main five parameters are studied. \textit{N\_estimators} defines the maximum number of allowed decision trees to be developed, and \textit{Max. depth} defines the complexity of the decision-tree structure. \textit{Subsample} controls the fraction of total event samples for each boosting procedure, \textit{learning rate} weights a decision tree to be added onto the current model, and \textit{gamma} regulates the evaluation of each decision tree.

>>>>

The toy sampling calorimeter is designed as a block consisting of alternating layers of an 1-mm-thick lead absorber and a 5-mm-thick polyvinyltoluene-based plastic scintillator. The plastic scintillator is segmented into 15-mm-wide strips, which are alternately oriented in the vertical and horizontal directions, as shown in Figure~\ref{fig:det_conf}. It has a cross-section size of 525~$\times$~525~mm$^{2}$ and accommodates 105 alternating layers of 630~mm and 20 radiation lengths (20$X_{0}$) to contain the EM shower of photons for energies in the range of 0.1 to 2~GeV.

@@

The incident angle of the photons is reconstructed using XGB~\cite{xgboost:2016}, which maps a feature dataset, the energy deposit in each scintillator strip, onto a target variable, the incident angle of a photon. The feature size identical to the number of strips varies with the strip width to have the same coverage. In the case of the 15-mm-wide strips, 35~$\times$~105 channels compose the detector. XGB constructs gradient-boosted decision trees using the training dataset, efficiently descending the loss function. The hyperparameters of XGB drive how models are trained. In this paper, main five parameters are studied. \textit{N\_estimators} defines the maximum number of allowed decision trees to be developed, and \textit{Max. depth} defines the complexity of the decision-tree structure. \textit{Subsample} controls the fraction of total event samples for each boosting procedure, \textit{learning rate} weights a decision tree to be added onto the current model, and \textit{gamma} regulates the evaluation of each decision tree.
